\chapter{Literature Survey}
\chapterdecscription{
Brief summary of contents,\\
Relation to your topic: how does the work described in the reference differ from your approach, what results have they obtained, what open questions do they still have?\\
A guideline is to include between 10 and 20 papers on your topic in the survey. The exact number depends on the topic and available literature.
}
\temporary{
\section{To Read}
\begin{itemize}
\item \cite{clarke2006applications} About the applications of water column data. I think we need to know what the (most popular) applications of water column data are in order to do a proper data set selection for the experiment.
\item \cite{biji2016benchmark} About the creation of a benchmark set in a whole different field (genetics). Seems interesting to see which methods the authors have applied and why.
%\item \cite{guo2014benchmarking} Benchmarking for graph processing, a vision.
\item \cite{capotua2015graphalytics} The actual benchmark for graph processing.
%\item \cite{beamer2015gap} Another benchmark for graph processing. This one from Berkeley.
\item \cite{swacha2008cote} About CoTe, the tool references in \cite{swacha2008assessing}. 
\item \cite{powell2001evaluating} About a benchmark created based on the Cantenbury corpus. It is interesting to if we can find out if they have problems with people wanting to hand over their algorithms and if they did something to prevent tailoring to the corpus.
\item \cite{patel2015rethinking} Paper about the problems with benchmarks 'now a days'. Probably not the most interesting paper ever, but it could contain some interesting points.

\end{itemize}
}
\section{Building a Corpus/benchmark suite}
	\subsection{The GAP Benchmark suite, Beamer et al.}    \input{chapters/literature/The_GAP_Benchmark_Suite}
	\subsection{A corpus for the evaluation of lossless compression algorithms, Arnold \& Bell}	\input{chapters/literature/A_corpus_for_the_evaluation_of_lossless_compression_algorithms}    
    \temporary{\subsection{Corpus for comparing compression methods and an extension of a ExCom library}
		\input{chapters/literature/Corpus_for_comparing_compression_methods_and_an_extension_of_a_ExCom_library}}
	\subsection{A Benchmark Framework for Data Compression Techniques, Damme et al.}
		\input{chapters/literature/A_Benchmark_Framework_for_Data_Compression_Techniques}
    \subsection{Assessing the Efficiency of Data Compression and Storage System, Swacha}
		\input{chapters/literature/Assessing_the_Efficiency_of_Data_Compression_and_Storage_System}
        
\subsection{Benchmarking graph-processing platforms: A vision, Guo et al.}
\input{chapters/literature/Benchmarking_graph-processing_platforms_a_vision}
\subsection{Graphalytics: A big data benchmark for graph-processing platforms, Capot{\u{a}} et al.}
	\input{chapters/literature/Graphalytics__A_big_data_benchmark_for_graph-processing_platforms}
        
\section{Applications of water column data}
	\subsection{Computational challenges in processing and analysis of full watercolumn multibeam sonar data, Buelens et al.}
		\input{chapters/literature/Computational_challenges_in_processing_and_analysis_of_full-watercolumn_multibeam_sonar_data}

\section{Compression algorithms}
	\subsection{Real-time lossless compression of multibeam echosounder water column data, Amblas et al.}
		\input{chapters/literature/Real-time_lossless_compression_of_multibeam_echosounder_water_column_data__Amblas_et_al}
	\subsection{A novel method for archiving multibeam sonar data with emphasis on efficient record size reduction and storage, Moszynski et al.}
    	\input{chapters/literature/A_novel_method_for_archiving_multibeam_sonar_data_with_emphasis_on_efficient_record_size_reduction_and_storage__Moszynski_et_al}
	\subsection{Application of {JPEG} 2000 wavelet compression to multibeam echosounder mid-water acoustic reflectivity measurements, Beaudoin}
    	\input{chapters/literature/Application_of__JPEG__2000_wavelet_compression_to_multibeam_echosounder_mid-water_acoustic_reflectivity_measurements__Beaudoin}

